XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/paper.tex
migrate to newer sigplan cls

%\documentclass{acm_proc_article-sp}
\documentclass{sig-alternate}

\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{ulem}
\usepackage{xspace}
\usepackage[scaled=0.8]{beramono}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{listings}

\input{code/style.tex}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  language=Python,
  keywordstyle=\bfseries,
  stringstyle=\color{blue},
  commentstyle=\color{gray}\textit,
  fancyvrb=true,
  showstringspaces=false,
  %keywords={def,while,if,elif,return,class,get,set,new,guard_class}
  numberstyle = \tiny,
  numbersep = -20pt,
}

@@

\numberofauthors{4}
\author{
\alignauthor Carl Friedrich Bolz\\
       \affaddr{University of Düsseldorf}\\
       \affaddr{STUPS Group}\\
       \affaddr{Germany}\\
       \email{cfbolz@gmx.de}
\alignauthor XXX
       \affaddr{XXX}\\
       \email{XXX}
}
\conferenceinfo{ICOOOLPS}{'09 Genova, Italy}
\CopyrightYear{2009}
\crdata{978-1-60558-541-3/09/07}

>>>>

\documentclass{sigplanconf}

\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}

\usepackage{listings}

\usepackage[T1]{fontenc}
\usepackage[scaled=0.8]{beramono}

\definecolor{commentgray}{rgb}{0.3,0.3,0.3}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  language=Python,
  keywordstyle=\bfseries,
  stringstyle=\color{blue},
  commentstyle=\color{commentgray}\textit,
  fancyvrb=true,
  showstringspaces=false,
  %keywords={def,while,if,elif,return,class,get,set,new,guard_class}
  numberstyle = \tiny,
  numbersep = -20pt,
}

@@

\authorinfo{Carl Friedrich Bolz \and XXX}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {cfbolz@gmx.de \and XXX}

\conferenceinfo{ICOOOLPS}{'11 Lancaster, UK}
\CopyrightYear{2011}
\crdata{XXX}
